---
title: "Negative Partner Correlations: Binary brms/glmmTMB Stress Tests"
output:
  html_document:
    toc: true
    df_print: paged
---

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 4
)

suppressPackageStartupMessages({
  library(brms)
  library(glmmTMB)
  library(knitr)
})

options(mc.cores = min(2, parallel::detectCores()))
brms_backend <- if (requireNamespace("cmdstanr", quietly = TRUE)) "cmdstanr" else "rstan"

fit_brms <- function(formula, data, seed) {
  brm(
    formula = formula,
    data = data,
    family = bernoulli(link = "logit"),
    prior = c(
      prior(normal(0, 2), class = "b"),
      prior(student_t(3, 0, 1.5), class = "sd"),
      prior(lkj(2), class = "cor")
    ),
    chains = 2,
    cores = 2,
    iter = 600,
    warmup = 300,
    seed = seed,
    backend = brms_backend,
    refresh = 0,
    control = list(adapt_delta = 0.95)
  )
}

rmvn2 <- function(n, sd_1, sd_2, cor) {
  cov <- matrix(
    c(sd_1^2, cor * sd_1 * sd_2, cor * sd_1 * sd_2, sd_2^2),
    nrow = 2
  )
  matrix(rnorm(n * 2), ncol = 2) %*% chol(cov)
}

make_table <- function(rows) {
  rows[] <- lapply(rows, function(x) if (is.numeric(x)) round(x, 3) else x)
  kable(rows)
}

extract_glmm_us <- function(model, group) {
  vc <- VarCorr(model)$cond[[group]]
  c(
    sd_1 = unname(attr(vc, "stddev")[1]),
    sd_2 = unname(attr(vc, "stddev")[2]),
    cor_12 = unname(attr(vc, "correlation")[1, 2])
  )
}

extract_brms_us <- function(model, group) {
  s <- summary(model)$random[[group]]
  c(
    sd_1 = s["sd(is_male)", "Estimate"],
    sd_2 = s["sd(is_female)", "Estimate"],
    cor_12 = s["cor(is_male,is_female)", "Estimate"]
  )
}
```

For binary models, the covariance parameters are latent Gaussian random effects
on the logit scale. They are not observed-scale residual correlations.

These examples are intentionally treated as stress tests. With a single binary
outcome per partner and occasion, the lowest-level latent covariance is much
harder to identify than in Gaussian or count models. Boundary estimates or
larger package-to-package differences are therefore informative rather than
surprising.

## Cross-Sectional Distinguishable Dyads

This is the direct cross-sectional analogue of the non-Gaussian random-effect
formulation. Each dyad contributes only two binary observations, so the latent
correlation is expected to be weakly identified.

```{r cross-dist-bernoulli}
set.seed(3101)
n_couples <- 1200

beta <- c(is_male = -0.35, is_female = -0.65)
true_latent <- c(sd_1 = 1.2, sd_2 = 1.0, cor_12 = -0.7)
latent <- rmvn2(
  n_couples,
  true_latent["sd_1"],
  true_latent["sd_2"],
  true_latent["cor_12"]
)

df <- data.frame(
  coupleID = factor(rep(seq_len(n_couples), each = 2)),
  member = rep(1:2, n_couples),
  is_male = rep(c(1, 0), n_couples),
  is_female = rep(c(0, 1), n_couples)
)

df$latent <- ifelse(
  df$is_male == 1,
  rep(latent[, 1], each = 2),
  rep(latent[, 2], each = 2)
)
eta <- with(df, beta["is_male"] * is_male + beta["is_female"] * is_female + latent)
df$y <- rbinom(nrow(df), size = 1, prob = plogis(eta))

model_glmm <- glmmTMB(
  y ~ 0 + is_male + is_female +
    (0 + is_male + is_female | coupleID),
  data = df,
  family = binomial(link = "logit")
)

model_brms <- fit_brms(
  bf(
    y ~ 0 + is_male + is_female +
      (0 + is_male + is_female | coupleID)
  ),
  data = df,
  seed = 3101
)

make_table(data.frame(
  parameter = names(true_latent),
  true = unname(true_latent),
  glmmTMB = unname(extract_glmm_us(model_glmm, "coupleID")),
  brms = unname(extract_brms_us(model_brms, "coupleID"))
))
```

## ILD Distinguishable Dyads

The ILD example adds both a stable couple-level latent covariance and a
same-day partner covariance. The same-day block is the hardest part because
each couple-day contributes only one binary observation per partner.

```{r ild-dist-bernoulli}
set.seed(3102)
n_couples <- 180
n_days <- 4

beta <- c(is_male = -0.35, is_female = -0.65)
true_couple <- c(sd_1 = 0.9, sd_2 = 0.75, cor_12 = -0.55)
true_day <- c(sd_1 = 1.0, sd_2 = 0.85, cor_12 = -0.65)
couple_re <- rmvn2(
  n_couples,
  true_couple["sd_1"],
  true_couple["sd_2"],
  true_couple["cor_12"]
)

df <- expand.grid(
  coupleID = seq_len(n_couples),
  day = seq_len(n_days),
  member = 1:2
)
df <- df[order(df$coupleID, df$day, df$member), ]
df$coupleID <- factor(df$coupleID)
df$couple_day <- interaction(df$coupleID, df$day, drop = TRUE)
df$is_male <- as.numeric(df$member == 1)
df$is_female <- as.numeric(df$member == 2)

day_re <- rmvn2(
  n_couples * n_days,
  true_day["sd_1"],
  true_day["sd_2"],
  true_day["cor_12"]
)
day_index <- (as.integer(df$coupleID) - 1) * n_days + df$day
df$couple_re <- ifelse(
  df$is_male == 1,
  couple_re[as.integer(df$coupleID), 1],
  couple_re[as.integer(df$coupleID), 2]
)
df$day_re <- ifelse(
  df$is_male == 1,
  day_re[day_index, 1],
  day_re[day_index, 2]
)
eta <- with(
  df,
  beta["is_male"] * is_male +
    beta["is_female"] * is_female +
    couple_re + day_re
)
df$y <- rbinom(nrow(df), size = 1, prob = plogis(eta))

model_glmm <- glmmTMB(
  y ~ 0 + is_male + is_female +
    (0 + is_male + is_female | coupleID) +
    (0 + is_male + is_female | couple_day),
  data = df,
  family = binomial(link = "logit")
)

model_brms <- fit_brms(
  bf(
    y ~ 0 + is_male + is_female +
      (0 + is_male + is_female | coupleID) +
      (0 + is_male + is_female | couple_day)
  ),
  data = df,
  seed = 3102
)

make_table(rbind(
  data.frame(
    block = "couple",
    parameter = names(true_couple),
    true = unname(true_couple),
    glmmTMB = unname(extract_glmm_us(model_glmm, "coupleID")),
    brms = unname(extract_brms_us(model_brms, "coupleID"))
  ),
  data.frame(
    block = "same-day latent",
    parameter = names(true_day),
    true = unname(true_day),
    glmmTMB = unname(extract_glmm_us(model_glmm, "couple_day")),
    brms = unname(extract_brms_us(model_brms, "couple_day"))
  )
))
```
