---
title: "Moderation Test"
author: "Pascal Küng"
date: "last-modified"
format:
  html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
gc()
library(glue)
```

## Overview

* Distinguishable Dyads
  * Cross-Sectional APIM
  * Longitudinal APIM
  
* Exchangeable Dyads
  * Cross-Sectional APIM
  * Cross-Sectional DIM
  * Equivalence between APIM and DIM
  * Longitudinal DIM
  * Longitudinal APIM
  
## Loading Libraries and setting CmdStan Backend

Some functions used in this presentation are sourced from the files available
in the folder 00_R_Functions.

```{r, results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(brms)
library(bmlm)
library(easystats)
library(DiagrammeR)
library(DHARMa)
library(MASS)
library(purrr)
source(file.path('00_R_Functions', 'ReportModels.R'))
source(file.path('00_R_Functions', 'PrettyTables.R'))
source(file.path('00_R_Functions', 'PrepareData.R'))

options(
  brms.backend = 'cmdstan',
  brms.file_refit = 'on_change'
)
```


## Distinguishable Dyads - L-APIM - Simulated Dataset

```{r echo=FALSE, results='hide'}
# Simulate Data
set.seed(123)

# ===============================
# 1) Design
# ===============================
n_couples <- 100
days      <- 0:54 
T_per     <- length(days)

# People per couple: p1 = female, p2 = male
persons <- tibble(
  coupleID  = rep(1:n_couples, each = 2),
  p_num     = rep(1:2, times = n_couples),
  gender    = ifelse(p_num == 1, 1L, 2L),  # 1=female, 2=male
  is_female = as.integer(gender == 1L),
  is_male   = as.integer(gender == 2L),
  userID    = paste0(coupleID, "_", p_num)
)

# ===============================
# 2) Fixed effects (edit as desired)
# ===============================
# Intercepts & time trends by gender
b0_female <- 5.5; b0_male <- 4.7 # depends on centering, not meaningful when recovered. 
b_time_female <-  0.01; b_time_male <- -0.005 # must be small because over 55 days!

# Between-person APIM (effects of person-mean support)
b_bp_actor_f <- 1.5; b_bp_partner_f <- 0.5
b_bp_actor_m <- 1.2; b_bp_partner_m <- 0.3

# Within-person APIM (effects of daily deviations)
b_wp_actor_f <- 0.4; b_wp_partner_f <- 0.2
b_wp_actor_m <- 0.2; b_wp_partner_m <- 0.1 # hard to detect!

# Cross-level interactions (stronger, differently sized)
b_int_actor_cwp_cbp <- 1.2
b_int_actor_cwp_partner_cbp <- 2.1

# ===============================
# 3) Couple-level random effects (full var-cov)
#    Vector: [b0_m, b0_f, time_m, time_f, wpA_m, wpP_m, wpA_f, wpP_f]
# ===============================
sd_re <- c(0.70, 0.80, 0.015, 0.015, 0.10, 0.08, 0.10, 0.08)
R     <- matrix(0.15, 8, 8); diag(R) <- 1
Sigma_re <- diag(sd_re) %*% R %*% diag(sd_re)

RE <- MASS::mvrnorm(n_couples, mu = rep(0, 8), Sigma = Sigma_re) |>
  as_tibble(.name_repair = ~c("re_b0_m","re_b0_f","re_time_m","re_time_f",
                              "re_wpA_m","re_wpP_m","re_wpA_f","re_wpP_f")) |>
  mutate(coupleID = 1:n_couples)

# ===============================
# 4) Provided support (predictor)
#    - Person means correlated within couple
#    - Daily AR(1) within-person; cross-partner correlated innovations
# ===============================
mu_sup_f <- 5.0; sd_mu_f <- 0.8
mu_sup_m <- 4.8; sd_mu_m <- 0.8
rho_couple_mean <- 0.50
Sigma_mu <- matrix(c(sd_mu_f^2, rho_couple_mean*sd_mu_f*sd_mu_m,
                     rho_couple_mean*sd_mu_f*sd_mu_m, sd_mu_m^2), 2)

mu_pairs <- MASS::mvrnorm(n_couples, mu = c(mu_sup_f, mu_sup_m), Sigma = Sigma_mu)

mu_df <- tibble(
  coupleID = rep(1:n_couples, each = 2),
  p_num    = rep(1:2, times = n_couples),
  mu_sup   = c(rbind(mu_pairs[,1], mu_pairs[,2]))
)

phi_sup <- 0.4
sd_sup_wp  <- 0.8
sd_eta_sup <- sqrt(sd_sup_wp^2 * (1 - phi_sup^2))
rho_sup_day <- 0.3
Sigma_eta_day <- matrix(c(sd_eta_sup^2, rho_sup_day*sd_eta_sup^2,
                          rho_sup_day*sd_eta_sup^2, sd_eta_sup^2), 2)

sim_support_one_couple <- function(cid) {
  eta <- MASS::mvrnorm(T_per, mu = c(0,0), Sigma = Sigma_eta_day)
  sup <- matrix(NA_real_, nrow = T_per, ncol = 2)
  sup[1,] <- eta[1,] / sqrt(1 - phi_sup^2)  # stationary init
  for (t in 2:T_per) sup[t,] <- phi_sup * sup[t-1,] + eta[t,]
  tibble(coupleID = cid, diaryday = days, sup_f = sup[,1], sup_m = sup[,2])
}

support_time <- purrr::map_dfr(1:n_couples, sim_support_one_couple)

support_long <- support_time |>
  tidyr::pivot_longer(c(sup_f, sup_m), names_to = "who", values_to = "sup_cwp") |>
  dplyr::mutate(p_num = ifelse(who == "sup_f", 1L, 2L)) |>
  dplyr::select(-who) |>
  dplyr::left_join(mu_df, by = c("coupleID","p_num")) |>
  dplyr::mutate(provided_support = mu_sup + sup_cwp) |>
  dplyr::select(coupleID, diaryday, p_num, provided_support, sup_cwp)

# ===============================
# 5) Assemble panel & partner lookups (safe keys)
# ===============================
panel <- tidyr::expand_grid(coupleID = 1:n_couples, diaryday = days, p_num = 1:2) |>
  dplyr::left_join(persons, by = c("coupleID","p_num")) |>
  dplyr::left_join(support_long, by = c("coupleID","diaryday","p_num"))

panel <- panel |>
  dplyr::group_by(coupleID, diaryday) |>
  dplyr::mutate(
    provided_support_partner = provided_support[3 - p_num],
    sup_cwp_partner          = sup_cwp[3 - p_num]
  ) |>
  dplyr::ungroup()

mu_actor_tbl   <- mu_df |> dplyr::rename(mu_actor = mu_sup)
mu_partner_tbl <- mu_df |> dplyr::mutate(p_num = 3 - p_num) |> dplyr::rename(mu_partner = mu_sup)

panel <- panel |>
  dplyr::left_join(mu_actor_tbl,   by = c("coupleID","p_num")) |>
  dplyr::left_join(mu_partner_tbl, by = c("coupleID","p_num"))

# ===============================
# 6) Same-day couple×day random effect (common shocks)
# ===============================
use_day_RE <- TRUE     # set FALSE to remove same-day shock
sd_day <- 0.17
if (use_day_RE) {
  day_shock <- tidyr::expand_grid(coupleID = 1:n_couples, diaryday = days) |>
    dplyr::mutate(z_day = rnorm(n(), 0, sd_day))
  panel <- panel |> dplyr::left_join(day_shock, by = c("coupleID","diaryday"))
} else {
  panel <- panel |> dplyr::mutate(z_day = 0)
}

# ===============================
# 7) Deterministic mean of daily closeness
# ===============================
grand_mu <- mean(mu_df$mu_sup)  # single grand mean for CBP

panel <- panel |>
  dplyr::left_join(RE, by = "coupleID") |>
  dplyr::mutate(
    # fixed parts by gender
    fix_b0   = ifelse(is_male==1, b0_male, b0_female),
    fix_time = ifelse(is_male==1, b_time_male, b_time_female),
    fix_bp_actor   = ifelse(is_male==1, b_bp_actor_m,  b_bp_actor_f),
    fix_bp_partner = ifelse(is_male==1, b_bp_partner_m,b_bp_partner_f),
    fix_wp_actor   = ifelse(is_male==1, b_wp_actor_m,  b_wp_actor_f),
    fix_wp_partner = ifelse(is_male==1, b_wp_partner_m,b_wp_partner_f),

    # couple-level REs by gender
    re_b0      = ifelse(is_male==1, re_b0_m,   re_b0_f),
    re_time    = ifelse(is_male==1, re_time_m, re_time_f),
    re_wp_actor= ifelse(is_male==1, re_wpA_m,  re_wpA_f),
    re_wp_part = ifelse(is_male==1, re_wpP_m,  re_wpP_f),

    # latent components
    actor_cwp   = sup_cwp,
    partner_cwp = sup_cwp_partner,
    actor_cbp   = mu_actor   - grand_mu,
    partner_cbp = mu_partner - grand_mu,

    # deterministic mean
    mu_it =
      fix_b0 + fix_time * diaryday +
      fix_bp_actor   * actor_cbp   + fix_bp_partner * partner_cbp +
      fix_wp_actor   * actor_cwp   + fix_wp_partner * partner_cwp +
      b_int_actor_cwp_cbp * actor_cwp * actor_cbp +
      b_int_actor_cwp_partner_cbp * actor_cwp * partner_cbp +
      re_b0 + re_time * diaryday +
      re_wp_actor * actor_cwp + re_wp_part * partner_cwp +
      z_day
  )

# ===============================
# 8) Residuals: AR(1) within person, gender-specific σ
# ===============================
phi_eps <- 0.10
sd_eps_f <- 0.70; sd_eps_m <- 1.10
sd_eta_f <- sqrt(sd_eps_f^2 * (1 - phi_eps^2))
sd_eta_m <- sqrt(sd_eps_m^2 * (1 - phi_eps^2))

simulate_ar1_resid <- function(n, sd_eta, phi=phi_eps) {
  e <- numeric(n)
  e[1] <- stats::rnorm(1, 0, sd = sd_eta / sqrt(1 - phi^2))
  if (n >= 2) for (t in 2:n) e[t] <- phi * e[t-1] + stats::rnorm(1, 0, sd_eta)
  e
}

# Vectorized generation per user
idx <- panel |>
  dplyr::arrange(userID, diaryday) |>
  dplyr::distinct(userID, is_male)

eps_list <- mapply(
  FUN = simulate_ar1_resid,
  n = T_per,
  sd_eta = ifelse(idx$is_male==1, sd_eta_m, sd_eta_f),
  SIMPLIFY = FALSE
)
eps_vec <- unlist(eps_list, use.names = FALSE)

panel <- panel |>
  dplyr::arrange(userID, diaryday) |>
  dplyr::mutate(e_it = eps_vec) |>
  dplyr::arrange(coupleID, diaryday, p_num)

# ===============================
# 9) Outcomes & exports
# ===============================
df_long <- panel |>
  dplyr::mutate(closeness = mu_it + e_it) |>
  dplyr::select(userID, coupleID, diaryday, gender,
                closeness, provided_support) |>
  dplyr::arrange(coupleID, userID, diaryday)

```


```{r echo = FALSE, results='hide', warning=FALSE, message=FALSE}

df_long_apim <- df_long %>% 
  reshape_dyadic_data(
    person_id = 'userID',
    dyad_id = 'coupleID',
    time = 'diaryday',
    vars_to_reshape = c('provided_support')
  ) %>%
  mutate(
    is_female = ifelse(gender == 1, 1, 0), 
    is_male = ifelse(gender ==2, 1, 0),
    diaryday_c = diaryday - mean(diaryday)
  ) %>% 
  dplyr::select(
    userID, coupleID, diaryday, diaryday_c, gender, is_male, is_female, closeness, provided_support_actor, provided_support_partner
  )


```


```{r echo = FALSE, results='hide', warning=FALSE, message=FALSE}

# Function for previev (not needed for analysis!)
print_couple_preview <- function(df, couple_id,
                                 days = 0:3) {
  # Filter/sort/select with original types
  dfc0 <- df %>%
    dplyr::filter(coupleID == couple_id) %>%
    dplyr::arrange(userID, diaryday)

  # Identify partners
  partners <- dfc0 %>%
    dplyr::distinct(userID) %>%
    dplyr::arrange(userID) %>%
    dplyr::pull(userID)

  if (length(partners) < 2)
    stop("This couple doesn't have two partners in the data.")

  # Slice by partner & day BEFORE coercion
  p1 <- dfc0 %>% dplyr::filter(userID == partners[1], diaryday %in% days)
  p2 <- dfc0 %>% dplyr::filter(userID == partners[2], diaryday %in% days)

  # Coerce everything to character explicitly (belt-and-suspenders on coupleID)
  to_chr <- function(x) x %>%
    dplyr::mutate(
      dplyr::across(where(is.numeric), ~round(., 2)), 
      dplyr::across(dplyr::everything(), as.character),
      coupleID = as.character(coupleID)
      )

  p1c <- to_chr(p1)
  p2c <- to_chr(p2)

  # 1-row "..." tibble with same columns (all character)
  colset <- names(dfc0)
  ellipsis_row <- tibble::as_tibble(setNames(rep(list("..."), length(colset)), colset))

  dplyr::bind_rows(p1c, ellipsis_row, p2c)
}


```


```{r echo=FALSE}

print_df(print_couple_preview(df_long_apim, couple_id = "31"))  

```


## Centering 

```{r}
df_long_apim <- bmlm::isolate(
  df_long_apim, 
  by = 'userID', # NOT coupleID
  value = c('provided_support_actor', 'provided_support_partner'),
  which = 'both' 
) %>%
# renaming to avoid confusion with between- and within COUPLE centred DIM variables
  rename(
    provided_support_actor_cwp = provided_support_actor_cw,
    provided_support_partner_cwp = provided_support_partner_cw,
    provided_support_actor_cbp = provided_support_actor_cb,
    provided_support_partner_cbp = provided_support_partner_cb,
  ) %>%
  # Centering time
  mutate(
    diaryday_c = scale(diaryday, center = TRUE, scale = FALSE)
  )

```



```{r echo=FALSE, results='hide'}

df_long_apim2 <- df_long_apim[,c('userID', 'coupleID', 'diaryday', 'diaryday_c', 'closeness', 'provided_support_actor', 'provided_support_partner', 'provided_support_actor_cbp', 'provided_support_actor_cwp', 'provided_support_partner_cbp', 'provided_support_partner_cwp')]

```


```{r echo=FALSE}

print_df(print_couple_preview(df_long_apim2, couple_id = "31"))  

```


## Exchangeable Dyads - Longitudinal DIM/APIM

* We need an APIM or DIM on both the between person level and the within-person level.
* Due to equivalence, we could have a DIM on one level and an APIM on the other. 

If we want a within-person DIM:

```{r}
df_long_dim <- df_long_apim2 %>%
  mutate(
    
    # Between Person Level DIM (centering between couples and within couple between person)
    provided_support_cbc = (provided_support_actor_cbp + provided_support_partner_cbp) / 2,
    provided_support_cwcbp = (provided_support_actor_cbp - provided_support_partner_cbp) / 2,
    
    # Within Person Level DIM (couple mean and deviation on each day)
    provided_support_cwp_mean = (provided_support_actor_cwp + provided_support_partner_cwp) / 2,
    provided_support_cwp_halfdiff = (provided_support_actor_cwp - provided_support_partner_cwp) / 2
  ) 


```

## Exchangeable Dyads - Longitudinal DIM/APIM: Preparing the Mean-Deviation Idiff Approach

We need to randomly assign -1 and +1 for each Partner within each couple. 
This will be needed for contrast coding the intercept. 

For example:

```{r eval = FALSE}

df_long_dim <- df_long_dim %>%
  group_by(coupleID) %>%
  mutate(
    base = ifelse(userID == min(userID), 1, -1),
    flip = 1 - 2 * rbinom(1, 1, 0.5),   # yields +1 or -1 once per couple
    Idiff = base * flip
  ) %>%
  ungroup() %>%
  relocate(Idiff, .after = coupleID) %>%
  dplyr::select(-base, -flip)


print_df(print_couple_preview(df_long_dim, couple_id = "31"))  

```


## Exchangeable Dyads - Longitudinal DIM/APIM: Preparing the Mean-Deviation Idiff Approach

```{r echo=FALSE}
set.seed(123)
df_long_dim <- df_long_dim %>%
  group_by(coupleID) %>%
  mutate(
    base = ifelse(userID == min(userID), 1, -1),
    flip = 1 - 2 * rbinom(1, 1, 0.5),   # yields +1 or -1 once per couple
    Idiff = base * flip
  ) %>%
  ungroup() %>%
  relocate(Idiff, .after = coupleID) %>%
  dplyr::select(-base, -flip)


print_df(print_couple_preview(df_long_dim, couple_id = "31", days = 0:4))  

```

## Exchangeable Dyads - Longitudinal APIM/DIM: Model

```{r }

formula <- bf(
  closeness ~ 1 + 
    
    diaryday_c +
  
    # Within-person APIM
    provided_support_actor_cwp + 
    provided_support_partner_cwp +
    # Equivalent to within-person DIM:
    # provided_support_cwp_mean + 
    # provided_support_cwp_halfdiff +
  
    # Between-person APIM
    provided_support_actor_cbp +
    provided_support_partner_cbp +
    # NEW cross-level interactions (person as context / partner as context) for the actor!
    provided_support_actor_cwp:provided_support_actor_cbp +
    provided_support_actor_cwp:provided_support_partner_cbp +
    # Equivalent to between-person DIM
    # provided_support_cwcbp+
    # provided_support_cbc +
    
    # Dyad-Level intercept and slopes for time-varying predictors
    (1 + diaryday_c + provided_support_actor_cwp + provided_support_partner_cwp | coupleID) +
    # Both partners' deviations from these dyad-level means and slopes.
    # Note: separate random effects block to make them uncorrelated form dyad-level REs. 
    (0 + Idiff + 
         I(Idiff * diaryday_c) + 
         I(Idiff * provided_support_actor_cwp) + 
         I(Idiff * provided_support_partner_cwp) | coupleID) +
    
    # Accounting for same-day shocks/coupling
    (1 | coupleID:diaryday)
    
    # Autocorrelated residuals
    # Due to bad fit in the distinguishable case, we omit AR1 from the start.
    # ar(time = diaryday, gr = coupleID:userID, p = 1)
  
  # Again, no need to model heterogeneous residual variances (sigma)
  # Implied: sigma = ~ 1
)

priors <- c(
  prior(normal(4, 2), class = "Intercept"),
  prior(normal(0, 2), class = "b")
  
  # We could set priors for other things, but brms sets good default priors
  #prior(student_t(3, 0, 1.5), class = "sd"),
  #prior(lkj(2), class = "cor"), # correlation prior for random effect matrix
  #prior(student_t(3, 0, 1.5), class = "sigma")
)

model_apim_ind_long <- brm(
  formula = formula, 
  data = df_long_dim,
  family = gaussian(link = identity),
  prior = priors,
  chains = 4,
  cores = 4,
  iter = 2000,
  warmup = 1000, 
  seed = 123,
  file = file.path('brms_cache', 'model_apim_ind_long_apim_context')
)


```

```{r echo=FALSE, results='hide', message=FALSE}

# DIM Version
formula <- bf(
  closeness ~ 1 + 
    
    diaryday_c +
    
    # Within-person APIM
    provided_support_actor_cwp + 
    provided_support_partner_cwp +
  
    # Between-person DIM
    provided_support_cbc +
    provided_support_cwcbp +
    
    # NEW cross-level interactions (couple as context / Equity as context) For the actor!
    provided_support_actor_cwp:provided_support_cbc +
    provided_support_actor_cwp:provided_support_cwcbp +
    
    (1 + diaryday_c + provided_support_actor_cwp + provided_support_partner_cwp | coupleID) +
    (0 + Idiff + 
         I(Idiff * diaryday_c) + 
         I(Idiff * provided_support_actor_cwp) + 
         I(Idiff * provided_support_partner_cwp) | coupleID) +
    
    (1 | coupleID:diaryday)
)

priors <- c(
  prior(normal(4, 2), class = "Intercept"),
  prior(normal(0, 2), class = "b")
)

model_dim_ind_long <- brm(
  formula = formula, 
  data = df_long_dim,
  family = gaussian(link = identity),
  prior = priors,
  chains = 4,
  cores = 4,
  iter = 2000,
  warmup = 1000, 
  seed = 123,
  file = file.path('brms_cache', 'model_apim_ind_long_dim_context')
)


```



```{r echo = FALSE}
summary_apim <- summarize_brms(
    model_apim_ind_long, 
    stats_to_report = c('CI', 'Rhat', 'ESS')
    )

print_df(
  summary_apim[1:8,1:2], 
  rows_to_pack = list(
    'Fixed Effects' = c(1,8)
    )
  )

```
b_int_actor_cwp_cbp <- 0.8
b_int_actor_cwp_partner_cbp <- 0.4

```{r echo = FALSE}
summary_apim <- summarize_brms(
    model_dim_ind_long, 
    stats_to_report = c('CI', 'Rhat', 'ESS')
    )

print_df(
  summary_apim[1:8,1:2], 
  rows_to_pack = list(
    'Fixed Effects' = c(1,8)
    )
  )

```


## Extract Full APIM Random Effects Variance-Covariance Matrix

We can rotate the random effects structure back to obtain the full APIM Random effects variance-covariance matrix. 
Just as we would in a SEM model with equality constraints!

For example, the within-partner variance of the random intercept is:

$$
\operatorname{Var}(u_{\text{common intercept}}) +
\operatorname{Var}(u_{\text{Idiff intercept}})
$$

and the cross-partner covariance of both partners' random intercepts is:

$$
\operatorname{Var}(u_{\text{common intercept}}) -
\operatorname{Var}(u_{\text{Idiff intercept}})
$$

In the model output, the common-intercept variance is labelled `Intercept`, and the deviation-intercept variance is labelled `Idiff`.
This rotation only holds when the common/couple-mean and `Idiff` deviation random effects are uncorrelated. This is why we put them in separate random-effects blocks.

## Extract Full APIM Random Effects Variance-Covariance Matrix

```{r}
# Custom function 
rotate_apim_covariance <- function(
    fit,
    gr = "coupleID",
    Idiff = "Idiff"
) {
  random_effects <- fit$ranef
  random_effects <- random_effects[random_effects$group == gr,]

  SUM <- random_effects$coef[!grepl(Idiff, random_effects$coef)]
  DIFF <- random_effects$coef[grepl(Idiff, random_effects$coef)]
  
  varcor <- VarCorr(fit)[[gr]]
  
  within_person_covariance_matrix <- varcor$cov[SUM,'Estimate',SUM] + varcor$cov[DIFF,'Estimate',DIFF]
  cross_person_covariance_matrix <- varcor$cov[SUM,'Estimate',SUM] - varcor$cov[DIFF,'Estimate',DIFF]
  
  p <- nrow(within_person_covariance_matrix)
  
  Full <- rbind(
    cbind(within_person_covariance_matrix,  cross_person_covariance_matrix),
    cbind(cross_person_covariance_matrix, within_person_covariance_matrix)
  )
  
  # nice labels
  base <- SUM
  rn <- c(paste0("PartnerA_", base), paste0("PartnerB_", base))
  colnames(Full) <- rn
  rownames(Full) <- rn
  
  return(list(within_person_covariance_matrix=within_person_covariance_matrix, cross_person_covariance_matrix=cross_person_covariance_matrix, full_covariance_matrix=Full))
}

a <- rotate_apim_covariance(model_apim_ind_long)

```

## Extract Full APIM Random Effects Variance-Covariance Matrix: Within-Person Matrix

```{r}
print_df(a$within_person_covariance_matrix)
```


## Extract Full APIM Random Effects Variance-Covariance Matrix: Cross-Person Matrix

```{r}
print_df(a$cross_person_covariance_matrix)
```


## Extract Full APIM Random Effects Variance-Covariance Matrix: Full Matrix

```{r}
print_df(a$full_covariance_matrix)
```


## Convert to correlation matrix of random effects

```{r}
# Custom function
sd_cor <- function(Sigma) {
  sds  <- sqrt(diag(Sigma))
  cors <- cov2cor(Sigma)  
  list(sd = sds, cor = cors)
}

full <- sd_cor(a$full_covariance_matrix)
```


## Random effects SDs

```{r}
print_df(as.data.frame(round(full$sd, 3)))
```

## Random effect correlation matrix

```{r}
print_df(as.data.frame(round(full$cor, 3)))
```


## References

```{r echo=FALSE, results='hide'}

pkgs <- c("brms","bmlm","easystats","DHARMa","tidyverse","cmdstanr","loo","rstan")

knitr::write_bib(pkgs, "Embed/Rpackages.bib")

```


